Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
French gos in italic + british-isation

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). The glyphs used in this dataset might be unknown to the OCR. Some of them, like
\scalerel*{\includegraphics{./images/LH.png}}{H}, do not even have a unicode codepoint. Text normalization is thus required
on the OCR outputs and consists in projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes
sense), homogenize extra symbols (star and hand symbols) and alleviate some ambiguities (e.g. \emph{no} and \emph{n°}).

At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalized} groundtruth text and the
OCR output is performed.

@@

\begin{table}
\caption{Entities to recognize in the dataset.}
\label{tab.entities}
\small
\begin{tabular}{llp{8cm}}
Entity & Count & Description\\    
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: "Alibert (Prosper)", "Allamand frères et Hersent", "Heurtemotte (Vve)", etc. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: "O. \scalerel*{\includegraphics{./images/LH.png}} {H}" for "Officier de la Légion d'Honneur" or "\scalerel*{\includegraphics{./images/GMLondon.png}}{H}" to represent the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarized in the single concept of activity. E.g.: "horlogerie", "export en tous genres", "Conseiller d'Etat", "propriétaire".\\
LOC & 9709 & mostly street names ("r. de la Jussienne"), but may also be neighborhoods ("Marais du Temple") or any indirect spatial references ("au Palais Royal").\\
CARDINAL & 8747 & a street number, as part of an address ("16", "5 bis"), or a range of numbers (e.g. "23-25" or "5 à 9").\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. "boutique", "atelier", "fab." or "dépôt". \\
\end{tabular}
\end{table}

>>>>

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). The glyphs used in this dataset might be unknown to the OCR. Some of them, like
\scalerel*{\includegraphics{./images/LH.png}}{H}, do not even have a unicode codepoint. Text normalisation is thus required
on the OCR outputs and consists in projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes
sense), homogenise extra symbols (star and hand symbols) and alleviate some ambiguities (e.g. \emph{no} and \emph{n°}).

At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed.

@@

\begin{table}
\caption{Entities to recognise in the dataset.}
\label{tab.entities}
\small
\begin{tabular}{llp{8cm}}
Entity & Count & Description\\    
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: \textit{Alibert (Prosper)}, \textit{Allamand frères et Hersent},\textit{Heurtemotte (Vve)}. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: O. \scalerel*{\includegraphics{./images/LH.png}} {H} for \textit{Officier de la Légion d'Honneur} or \scalerel*{\includegraphics{./images/GMLondon.png}}{H} for the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarised in the single concept of activity. E.g.: \textit{horlogerie}, \textit{export en tous genres}, \textit{Conseiller d'État}, \textit{propriétaire}.\\
LOC & 9709 & mostly street names (\textit{r. de la Jussienne}), but may also be neighbourhoods (\textit{Marais du Temple}) or any indirect spatial references (\textit{au Palais Royal}).\\
CARDINAL & 8747 & a street number, as part of an address (16, 5 bis), or a range of numbers (e.g. 23-25 or 5 \textit{à} 9).\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. \textit{boutique}, \textit{atelier}, \textit{fab.} or \textit{dépôt}. \\
\end{tabular}
\end{table}

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
French gos in italic + british-isation

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the french corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
In order to evaluate whether adapting CamemBERT to the domain increases its performances, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with Pero.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

>>>>

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the french corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Conclusion
French gos in italic + british-isation

% !TeX root = ../main-paper.tex
\section{Experiment 2: Impact of OCR noise on named entity recognition}
\label{sec:ner-xp2}
Noise introduced by OCR is known to have a negative impact on NER, because it alters the structure and lexicon of the input texts, moving them away from the language model known to the NER process.
In real-life situations, the models are often trained on texts without such noise, even though the texts to be annotated are extracted with OCR.
In this second experiment, we aim at assessing the most appropriate strategy to build a NER model tolerant to OCR noise.

@@

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by Pero-OCR feature characteristics intermediary between human transcriptions and Tesseract.
This OCR tool removes the characters recognised with low confidence, which is probably a great help to the NER.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}NER F1-scores in presence of OCR noise in the training and testing sets, grouped by test set. The dataset used for training is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}

>>>>

% !TeX root = ../main-paper.tex
\section{Impact of OCR noise on named entity recognition}
\label{sec:ner-xp2}
Noise introduced by OCR is known to have a negative impact on NER, because it alters the structure and lexicon of the input texts, moving them away from the language model known to the NER process.
In real-life situations, the models are often trained on texts without such noise, even though the texts to be annotated are extracted with OCR.
In this second experiment, we aim at assessing the most appropriate strategy to build a NER model tolerant to OCR noise.

@@

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by PERO-OCR feature characteristics intermediary between human transcriptions and Tesseract.
This OCR tool removes the characters recognised with low confidence, which is probably a great help to the NER.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}NER F1-scores in presence of OCR noise in the training and testing sets, grouped by test set. The dataset used for training is noted in indice after the model name (e.g. CmBERT$_{pero}$ for CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}

### 2022-01-20 src-latex/parts/80-conclusion.tex
Conclusion
French gos in italic + british-isation

% !TeX root = ../main-paper.tex
\section{Conclusion}
We assessed the performance of three modern OCR systems on real historical data.
Although Pero-OCR clearly outperforms its competitors, the qualitative analysis of OCR errors shows that the failure cases are not the same for Pero and Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model seems to be a good choice to serve as a bootstrapping model in order to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}

>>>>

% !TeX root = ../main-paper.tex
\section{Conclusion}
We assessed the performances of three modern OCR systems on a set of historical sources of great interest in social history.
Although PERO-OCR clearly outperforms its competitors, the qualitative analysis of OCR errors shows that the failure cases are not the same for PERO and Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model seems to be a good choice to serve as a bootstrapping model in order to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}
